\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[table]{xcolor}

\addtolength{\oddsidemargin}{-.5in}
\addtolength{\evensidemargin}{-.5in}
\addtolength{\textwidth}{1.0in}

\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\def\urltilda{\kern -.15em\lower .7ex\hbox{\~{}}\kern .04em}

\begin{document}

\begin{center}

\textbf{\large{ECON 379:  Program Evaluation for International Development}} \\

\bigskip

\textbf{\large{Empirical Exercise \#1}} \\ 
Due 2/25 by 11:30 AM 

\end{center}

\bigskip

\bigskip

This exercise makes use of the data set \texttt{E1-CohenEtAl-data.dta}, 
a subset of the data used in the paper ``Price Subsidies, 
Diagnostic Tests, and Targeting of Malaria Treatment: Evidence from a 
Randomized Controlled Trial'' by Jessica Cohen, Pascaline Dupas, and Simone 
Schaner, published in the \emph{American Economic Review} in 2015. 
The authors examine behavioral responses to various discounts (``subsidies'') 
for malaria treatment, called ``artemisinin combination therapy'' 
or ``ACT.''  

\bigskip

The aim of this empirical exercise is to review key Stata commands.
The data set used in this exercise is available at:  
\url{https://pjakiela.github.io/ECON379/exercises/E1-intro}.  You can 
also load the data into Stata directly using the \texttt{webuse} command:

\begin{verbatim}
webuse set https://pjakiela.github.io/ECON379/exercises/E1-intro/
webuse E1-CohenEtAl-data.dta
\end{verbatim}

\noindent
Download the data set, open it in Stata, and answer the following questions:

\begin{enumerate}
	
\item How many observations are in the data set?

\item The variable \texttt{act\_any} is a dummy for assignment to any treatment (positive subsidy) What is the mean of the variable \texttt{act\_any} (to three decimal places)?

\item How many people received a positive subsidy?

\item The variable \texttt{c\_act} is a dummy for using ACT treatment during a malaria episode.  
What is the standard deviation of the variable \texttt{c\_act}?

\item How many respondents report using ACT treatment for malaria?

\item Regress \texttt{c\_act} on \texttt{act\_any}.  What is the R-squared?

\item What is the coefficient associated with the \texttt{act\_any} variable?

\item What is the associated standard error?

\item What do you get when you divide the coefficient by the standard error?

\item What is the t-statistic associated with the \texttt{act\_any} variable?

\end{enumerate}


\end{document}
